---
output: github_document
---

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)](https://cran.r-project.org/)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/permDep)](https://cran.r-project.org/package=permDep)
[![packageversion](https://img.shields.io/badge/Package%20version-1.1.0-orange.svg?style=flat-square)](commits/master)
[![Travis-CI Build Status](https://travis-ci.org/stc04003/permDep.svg?branch=master)](https://travis-ci.org/stc04003/permDep)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/stc04003/permDep?branch=master&svg=true)](https://ci.appveyor.com/project/stc04003/permDep)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
 
## **permDep**

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

***permDep*** implements permutation approaches to test for quasi-independence in left-truncated right-censored survival data.

#### Installation

You can install and load **permDep** from CRAN using

```{r cran-installation, eval = FALSE}
install.packages("permDep")
library(permDep)
```

You can install permDep from github with:

```{r gh-installation, eval = FALSE}
## install.packages("devtools")
devtools::install_github("stc04003/permDep")
```

### Online documentation 
[Online document](https://www.sychiou.com/permDep/) includes a [demonstration](http://www.sychiou.com/permDep/articles/vig-permDep.html) of the main function, `permDep`.

#### References:
* Chiou, S.H., Qian, J., and Betensky, R.A. (2017). Permutation Test for General Dependent Truncation. \emph{Techreport}
* Tsai, W.Y., (1990). Testing the Assumption of Independence of Truncation Time and Failure Time. \emph{Biometrika} \bold{77} 169--177.
